Descriptive statistics

### 2023-01-05 Code/3_Descriptives.Rmd
Validation added
Median time, Q1, Q3 corrected

---
title: "Multiple imputation"
author: "Carolien C.H.M. Maas"
date: "December 2022"
output: html_document
---

@@

  # save in tab.time
  tab.time <- c("Total Development", paste(sprintf("%.2f", median.time.total$quantiles.survival[3, "quantile"]),
                   paste0("[", sprintf("%.2f", median.time.total$quantiles.survival[3, "lower"]), "; ",
                          sprintf("%.2f", median.time.total$quantiles.survival[3, "upper"]), "]")))

  # time per center
  for (center in c("Amsterdam", "Berlin", "Rotterdam", "Warsaw", "Australia")){
    med.table <- eval(parse(text=paste0("median.time$`Center=", center, "`")))
    med <- med.table[3,"quantile"]
    lower <- med.table[3,"lower"]
    upper <- med.table[3,"upper"]
    tab.time <- rbind(tab.time, c(center, paste(sprintf("%.2f", med), paste0("[", sprintf("%.2f", lower), "; ", sprintf("%.2f", upper), "]"))))
  }

>>>>

---
title: "Descriptive statistics"
author: "Carolien C.H.M. Maas"
date: "January 2023"
output: html_document
---

@@

  # save in tab.time
  tab.time <- c("Total Development", paste(sprintf("%.2f", median.time.total$quantiles.survival[3, "quantile"]),
                   paste0("[", sprintf("%.2f", median.time.total$quantiles.survival[4, "quantile"]), "; ",
                          sprintf("%.2f", median.time.total$quantiles.survival[2, "quantile"]), "]")))

  # time per center
  for (center in c("Amsterdam", "Berlin", "Rotterdam", "Warsaw", "Australia")){
    med.table <- eval(parse(text=paste0("median.time$`Center=", center, "`")))
    med <- med.table[3,"quantile"]
    lower <- med.table[4,"quantile"]
    upper <- med.table[2,"quantile"]
    tab.time <- rbind(tab.time, c(center, paste(sprintf("%.2f", med), paste0("[", sprintf("%.2f", lower), "; ", sprintf("%.2f", upper), "]"))))
  }
